Machine Learning for Predictive Auto-Tuning with Boosted Regression Trees

### 2012-03-13 paper/final.tex
hack a word-wrapping dash

One strategy for addressing these challenges is to use one of a variety of
automatic methods known collectively as ``auto-tuning.'' Two major auto-tuning
approaches have emerged in the extensive literature covering the subject (see
surveys in e.g.
\citep{vuduc2001statistical, demmel2005self, vuduc2005oski, williams2008auto,
datta2008stencil, cavazos2008intelligent, li2009note, park2011evaluation}):
analytical model-driven optimization and empirical optimization
\citep{yotov2003comparison}.

>>>>

One strategy for addressing these challenges is to use one of a variety of
automatic methods known collectively as ``auto-tuning.'' Two major auto-tuning
approaches have e-merged in the extensive literature covering the subject (see
surveys in e.g.
\citep{vuduc2001statistical, demmel2005self, vuduc2005oski, williams2008auto,
datta2008stencil, cavazos2008intelligent, li2009note, park2011evaluation}):
analytical model-driven optimization and empirical optimization
\citep{yotov2003comparison}.
